Occurrence and transmission potential of asymptomatic and pre-symptomatic SARS-CoV-2 infections: a living systematic review and meta-analysis

### 2021-10-29 Manuscript_draft.Rmd
Update Manuscript_draft.Rmd

dataG$label=ifelse(dataG$type==2,
                   paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)

>>>>

# dataG$label=ifelse(dataG$type==2,
#                    paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)

dataG$label=ifelse(dataG$label=="   Ganyani T",
                   paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)

dataG$label=ifelse(dataG$label=="   Peak CM",
                   paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
dataG$label=ifelse(dataG$label=="   Tindale LC",
                   paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)

dataG$label=ifelse(dataG$label=="   Zhang W",
                   paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)

dataG$label=ifelse(dataG$label=="   Casey M",
                   paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
